\bf Title here

### 2020-05-19 paper/paper.Rmd
knit again
bit on explore basis

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)

@@

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/holes_2d_pos.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))

@@

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

@@

load(here::here("data/temp.rda"))
load(here::here("data/data_mult.rda"))
load(here::here("data/holes_1d_geo.rda"))
load(here::here("data/holes_1d_geo_polish.rda"))
load(here::here("data/holes_2d_geo.rda"))
load(here::here("data/holes_2d_better.rda"))
load(here::here("data/holes_2d_better_max_tries.rda"))
load(here::here("data/holes_2d_better_random.rda"))
load(here::here("data/holes_2d_geo_polish.rda"))
load(here::here("data/holes_2d_better_polish.rda"))
load(here::here("data/holes_2d_better_max_tries_polish.rda"))
load(here::here("data/holes_2d_better_random_polish.rda"))
load(here::here("data/holes_2d_pos.rda"))
load(here::here("data/interrupt_yes.rda"))
load(here::here("data/interrupt_no.rda"))

@@

```{r echo = TRUE}
nrow(holes_2d_better_max_tries)
nrow(holes_2d_pos)
```

@@

The variable or object to explore could sometimes be a more than a scale, for example, in a tour, we would also be interested to explore the relative position of the projection basis in the vector space. This imposes difficulties in visualisation since as human, we are bounded to preceive at most three dimensions. Dimension reduction is reuqired to summarise the projection matrix to a managable number of variable to map to a plot. Principal copmonent analysis is used to extract the direction that reflects most variation in the data.

### 2020-05-19 paper/paper.tex
bit on explore basis

\begin{verbatim}
## # A tibble: 5 x 7
##   basis             index_val tries info              loop method             id
##   <list>                <dbl> <dbl> <chr>            <dbl> <chr>           <int>
## 1 <dbl[,1] [5 x 1]>     0.749     1 start               NA <NA>                1
## 2 <dbl[,1] [5 x 1]>     0.749     1 direction_search     1 search_geodesic     2
## 3 <dbl[,1] [5 x 1]>     0.749     1 direction_search     1 search_geodesic     3
## 4 <dbl[,1] [5 x 1]>     0.749     1 direction_search     1 search_geodesic     4
## 5 <dbl[,1] [5 x 1]>     0.749     1 direction_search     1 search_geodesic     5
\end{verbatim}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-8-1.pdf}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{()}
\end{Highlighting}
\end{Shaded}

@@

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-11-1.pdf}

>>>>

\begin{verbatim}
## # A tibble: 5 x 8
##   basis           index_val tries info            loop method        alpha    id
##   <list>              <dbl> <dbl> <chr>          <dbl> <chr>         <dbl> <int>
## 1 <dbl[,1] [5 x ~     0.749     1 start             NA <NA>            0.5     1
## 2 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       2
## 3 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       3
## 4 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       4
## 5 <dbl[,1] [5 x ~     0.749     1 direction_sea~     1 search_geode~  NA       5
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{nrow}\NormalTok{(holes_2d_better_max_tries)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 1531
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{nrow}\NormalTok{(holes_2d_pos)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 959
\end{verbatim}

@@

The variable or object to explore could sometimes be a more than a
scale, for example, in a tour, we would also be interested to explore
the relative position of the projection basis in the vector space. This
imposes difficulties in visualisation since as human, we are bounded to
preceive at most three dimensions. Dimension reduction is reuqired to
summarise the projection matrix to a managable number of variable to map
to a plot. Principal copmonent analysis is used to extract the direction
that reflects most variation in the data.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{holes_1d_geo }\OperatorTok{%>%}\StringTok{ }\KeywordTok{explore_proj_pca}\NormalTok{() }
\end{Highlighting}
\end{Shaded}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-10-1.pdf}

@@

\includegraphics{paper_files/figure-latex/unnamed-chunk-12-1.pdf}
